

\documentclass[letterpaper,11pt]{article}
\usepackage[LY1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{polski}
\usepackage{fourier}   
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\DeclareTextCompositeCommand{\k}{LY1}{a}
  {\oalign{a\crcr\noalign{\kern-.27ex}\hidewidth\char7}}
\DeclareTextCompositeCommand{\k}{LY1}{e}
  {\oalign{e\crcr\noalign{\kern-.27ex}\hidewidth\char7\hidewidth}}
\DeclareTextCompositeCommand{\k}{LY1}{E}
  {\oalign{E\crcr\hidewidth\char7\hidewidth}}

\DeclareTextCompositeCommand{\'}{LY1}{c}
  {{\ooalign{\hidewidth\raise-.13875ex\hbox{\'{}}\hidewidth\crcr c}}}
\DeclareTextCompositeCommand{\'}{LY1}{s}
  {{\ooalign{\hidewidth\raise-.13875ex\hbox{\'{}}\hidewidth\crcr s}}}
\DeclareTextCompositeCommand{\'}{LY1}{z}
  {{\ooalign{\hidewidth\raise-.13875ex\hbox{\'{}}\hidewidth\crcr z}}}
\DeclareTextCompositeCommand{\'}{LY1}{C}
  {{\ooalign{\hidewidth\raise.65367ex\hbox{\'{}}\hidewidth\crcr C}}}
\DeclareTextCompositeCommand{\'}{LY1}{S}
  {{\ooalign{\hidewidth\raise.65367ex\hbox{\'{}}\hidewidth\crcr S}}}
\DeclareTextCompositeCommand{\'}{LY1}{Z}
  {{\ooalign{\hidewidth\raise.65367ex\hbox{\'{}}\hidewidth\crcr Z}}}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Grzegorz Kmita} \\ \vspace{1pt}
    \small +48 576 566 560 $|$ \href{mailto:grzegorzkmita@tuta.io}{\underline{grzegorzkmita@tuta.io}} $|$
    \href{https://linkedin.com/in/grzegorzkmita}{\underline{linkedin.com/in/grzegorzkmita}} $|$
    \href{https://github.com/jirafey}{\underline{github.com/jirafey}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {West Pomeranian University of Technology}{Szczecin} 
      {Computer science engineer}{Jun 2022 -- Jul 2026}
      \resumeSubheading
    {Python, Microsoft Access, Excel course}{\href{https://encodeme-maturalnie.pl}
    {\underline{encodeme-maturalnie.pl}}}{Passed}{Jan 2022 -- May 2022}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    %grzegorzkmita.com%
        \resumeProjectHeading
          {\textbf{\href{https://grzegorzkmita.com}
    {\underline{grzegorzkmita.com}}}  $|$ {\href{https://github.com/jirafey/grzegorzkmita.com}
    {\underline{GitHub}}} $|$ \emph{HTML, CSS, JavaScript, Git, Vercel}}{2020 -- Present}
          \resumeItemListStart
            \resumeItem{I created a personal portfolio website with a minimalist front-end}
            \resumeItem{I have integrated Vercel with GitHub. Every \emph{git push} is followed by a website update if it passes all checks from Vercel.}
            \resumeItem{I have created a subpage dedicated to the colloquial Chinese words used in the game Teamfight Tactics.}
            \resumeItem{I have added graphics representing the items in game and their names, as well as popular vocabulary used by the Chinese}
          \resumeItemListEnd
          \resumeProjectHeading
       {\textbf {Program to manage personal data from a list} $|$ {\href{https://github.com/jirafey/pong}
    {\underline{GitHub}}} $|$ \emph{C, Git}}  {Feb 2023}
          \resumeItemListStart
                  \resumeItem{I built a program on a doubly linked list structure. I used dynamic memory allocation.}
        \resumeItem{I have implemented add/delete/save to file/read from file/sort (bubble)/search.}

      \resumeItemListEnd
              \resumeProjectHeading
                 {\textbf {Program multiplying matrices from a file} $|$ {\href{https://github.com/jirafey/pong}
    {\underline{GitHub}}} $|$ \emph{C, Git}}{Sty 2023}
          \resumeItemListStart
        \resumeItem{I created the program using pointers and dynamic memory allocation.}
        \resumeItem{I have implemented writing a matrix to a file, generating a random matrix, writing a random matrix to a txt file}
      \resumeItemListEnd
      \resumeProjectHeading
            %Square Madness%
          {\textbf {\href{https:jirafey.itch.io/square-madness}
    {\underline{Square Madness}}} $|$ {\href{https://github.com/jirafey/square-madness}
    {\underline{GitHub}}}  $|$ \emph{Python, pygame, Git}}{Cze 2022}
          \resumeItemListStart
            \resumeItem{\emph{Single-player 2D space shooter. Enemies follow the player in an attempt to obliterate him, while the player dodges enemy missiles and upgrades his ship.}}
            \resumeItem{I created a fully functional game menu, including audio and video settings (full screen/window).}
            \resumeItem{I added an ending, hints for the player, improved, among other things, the system of receiving damage, the UI and adjusted the difficulty level}
            \resumeItem{I composed the music, created the concept art and added SFX.}
          \resumeItemListEnd
      \resumeProjectHeading
            %Teacup Adventure%
                {\textbf {\href{https:jirafey.itch.io/teacup-adventure}
    {\underline{Teacup Adventure}}} $|$ {\href{https://github.com/jirafey/teacup-adventure}
    {\underline{GitHub}}} $|$ \emph{Python, pygame, Git}}{Lut 2022}
      \resumeItemListStart
        \resumeItem{\emph{Single-player 2D platformer with interesting mechanics - when the user jumps, a droplet flies out of the character, which must be picked up to jump again.}}
        \resumeItem{I composed the music, added SFX, created the graphics used in the game.}
        \resumeItem{I fixed the collision system and adjusted the difficulty level.}
      \resumeItemListEnd
      \resumeProjectHeading
      %Pong%
                    {\textbf {\href{https:jirafey.itch.io/pong}
    {\underline{Pong}}} $|$ {\href{https://github.com/jirafey/pong}
    {\underline{GitHub}}}  $|$ \emph{Python, turtle, Git}}{Lut 2022}
          \resumeItemListStart
        \resumeItem{\emph{Two-player local 2D game (Retro Pong) - 2 players use their paddles to bounce a ball, you have to punch the ball in such a way that the opponent does not manage to bounce it.}}
        \resumeItem{I programmed, among other things, the movement, collision system, combo and points system.}
        
      \resumeItemListEnd


    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Programming skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, HTML/CSS, JavaScript, {C{\#}}, Rust, Matlab, Arduino} \\
     \textbf{Technologoies}{: Access, Excel, GitHub, Git, Vercel, VS Code, Visual Studio, PyCharm, CLion, Unity, Markdown, LaTeX} \\
     \textbf{Libraries}{: pygame, turtle, NumPy, Pandas, Scikit-learn}
    }}
\end{itemize}
\section{Foregin languages}

\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Polish}{: native} \\
        \textbf{English}{: C1} \\
            \textbf{Chinese(Mandarin)}{: B1} \\
                \textbf{German}{: A2} \\
                    \textbf{Dutch}{: A1} \\

    }}
    \end{itemize}
%-------------------------------------------
\end{document}
